Appendix

### 2024-09-09 manuscript/manuscript_appendix.Rmd
Further improvements.
Work on improving real world example data.

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")
plot_theme$legend.key.size <- grid::unit(0.3, 'lines')
plot_theme$plot.tag <- ggplot2::element_text(
  size = ggplot2::rel(1.0),
  hjust = 0.0,
  vjust = 0.0,
  inherit.blank = FALSE
)
plot_theme$plot.tag.position <- c(0, 1)

@@

Other aspects of the experiment remain the same.
Thus, we first drew $m_d=10000$ random distributions.
For asymmetric generalised normal distributions, each distribution was parametrised with a randomly chosen skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$.
For fully normal distributions, skewness parameter $\alpha = 0.5$ and shape parameter $\beta = 2.0$ were fixed.
Location and scale parameters were set as $\mu = 0$ and $\sigma = 1$, respectively.
$n = \lceil 10^\gamma \rceil$ values were then randomly drawn, with $\gamma \sim U\left(1.47, 3.00\right)$, which led to between $30$ and $1000$ values being drawn to create $\mathbf{X}_i$.
Residuals were then computed after performing robust location- and scale-invariant transformations with the empirical tapered cosine weighting method for the dataset with asymmetric generalised normal distributions,
and without any transformation for the dataset with only normal distributions.

>>>>

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")
plot_theme$legend.key.size <- grid::unit(0.3, 'lines')
plot_theme$plot.tag <- ggplot2::element_text(
  size = ggplot2::rel(1.0),
  hjust = 0.0,
  vjust = 0.0,
  inherit.blank = FALSE
)
plot_theme$plot.tag.position <- c(0.2, 1)

@@

Other aspects of the experiment remained the same.
Thus, we first drew $m_d=10000$ random distributions.
For asymmetric generalised normal distributions, each distribution was parametrised with a randomly chosen skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$.
For fully normal distributions, skewness parameter $\alpha = 0.5$ and shape parameter $\beta = 2.0$ were fixed.
Location and scale parameters were set as $\mu = 0$ and $\sigma = 1$, respectively.
$n = \lceil 10^\gamma \rceil$ values were then randomly drawn, with $\gamma \sim U\left(1.47, 3.00\right)$, which led to between $30$ and $1000$ values being drawn to create $\mathbf{X}_i$.
Residuals were then computed after performing robust location- and scale-invariant transformations with the empirical tapered cosine weighting method for the dataset with asymmetric generalised normal distributions,
and without any transformation for the dataset with only normal distributions.
